\section{Sources}
The following sources were used during our preliminary research
for this project. Citations in the text above correspond to sources here.
\begin{enumerate}
\item ``Apache HTTP Server Documentation.'' 2012. Apache Software Foundation. \\ \href{http://httpd.apache.org/docs/}{http://httpd.apache.org/docs/}. (Technical documentation)
\item Chawla, Shuchi. ``Weighted Interval Scheduling Problem.'' Class lecture, University of Wisconsin-Madison, Madison, WI. (Algorithms)
\item Cormen, Thomas et al. {\em Introduction to Algorithms}. Cambridge: MIT Press, 2009. (Algorithms)
\item Darmann, Andreas et al. ``Group Activity Selection Problem.'' Paper presented at the 8\textsuperscript{th} International Workshop in Internet and Network Economics, Liverpool, United Kingdom, December 10-12, 2012. (Algorithms)
\item ``Flask Documentation.'' June 14, 2013. Flask Project. \href{http://flask.pocoo.org/docs/flask-docs.pdf}{http://flask.pocoo.org/docs/flask-docs.pdf}. (Technical documentation)
\item ``Getting Started.'' August 19, 2013. Bootstrap. \href{http://getbootstrap.com/2.3.2/getting-started.html}{http://getbootstrap.com/2.3.2/getting-started.html}. (Technical documentation)
\item Kolen, Antoon et al. ``Interval Scheduling: A Survey.'' {\em Wiley InterScience}, March 16, 2007. \href{http://www.econ.kuleuven.ac.be/public/NDBAE03/papers/nrl2007kolenpaper.pdf}{http://www.econ.kuleuven.ac.be/public/NDBAE03/papers/nrl2007kolenpaper.pdf}. (Algorithms)
\item ``Scheduleman.'' October 5, 2013. Scheduleman. \href{https://scheduleman.org}{https://scheduleman.org}. (Previous implementations)
\item ``schedule+.'' October 5, 2013. SchedulePlus. \href{http://scheduleplus.org}{http://scheduleplus.org}. (Previous implementations)
\item ``Schedule of Classes.'' August 2013. Carnegie Mellon University. \\ \href{https://enr-apps.as.cmu.edu/open/SOC/SOCServlet}{https://enr-apps.as.cmu.edu/open/SOC/SOCServlet}. (Data sources)
\item ``Student Information Online.'' October 2013. Carnegie Mellon University. \\ \href{https://s3.as.cmu.edu/sio/index.html}{https://s3.as.cmu.edu/sio/index.html}. (Previous implementations)
\end{enumerate}
