\section{Status}
We have built code that will scrape course numbers, meeting times,
professors, unit counts, prerequisites, corequisites, descriptions, and names.
Using this scraper, we have built a database of course information. This database
is accessible to browse at \url{http://spp.derig.org/depts/}.

We have also implemented many basic web application features (such as
registration and login) and a course search feature. This search can only
search classes that will run next semester and is available at
\url{http://spp.derig.org/search/}.

We have a bare-bones user interface and designs for a nicer interface which we
have sketched on paper but not yet implemented with HTML and CSS.

In addition, we have begun designing an algorithm to efficiently create schedules
that match a user's desired criteria. This algorithm is very important to the
functionality of the site, so we are taking care in designing it before we begin
to implement it. We believe that the design portion will be the hard part and
that once we have a good design actually writing the code should be fairly
straightforward.

We are slightly behind where we wanted to be at this point. Our
frontend is slightly more basic than we wanted it to be and we
are not quite as far along on the schedule optimizer as we had planned to be.
However, we have scraped data and populated content into our database. We are
starting to work on scheduling UI/UX, as we said we would do in our Gantt chart.
We're running slightly ahead of schedule on searching classes.
